---
title: "Function-on-Scalar Regression"
output:
  html_document: 
    code_folding: hide
    toc: true
    toc_float: true
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE
)
```

This page contains a combination of traditional lecture materials (slides) and code demonstrating the relevant methods. The short course will proceed by working through both. We will use several recent packages in our examples; see the [About](./About.html) page for information about the package versions.

```{r setup}
library(tidyverse)
library(grpreg)
library(splines)
library(refund)
library(refund.shiny)
```

In this section we'll use the [HeadStart data](./Data.html) to motivate the function-on-scalar regression model. Our main outcome of interest is the observed physical activity profile, with predictors including age, sex, and season. Below we plot activity profiles colored by sex.

```{r Accel_explore, eval = TRUE}
load("./DataCode/HeadStart.RDA")

as_refundObj(accel) %>% 
	left_join(dplyr::select(covariate_data, id, sex_female)) %>%
	ggplot(aes(x = index, y = value, group = id, color = sex_female)) + geom_path(alpha = .5)
```

## Function-on-scalar regression

Slides below introduce function-on-scalar regression.

PLACEHOLDER FOR SPEAKERDECK SLIDES

## Practical example

CODE BELOW NEEDS SUBSTANTIAL EDITING

To motivate the use of variable selection methods for this dataset, we can examine the results of an analysis that does not shrink coefficients. The code below fits such a model and shows all resulting coefficients; while there are some obvious large effects, many others are small and may not be necessary.

```{r Accel_varselect_motivate, eval = TRUE}
temp_df = covariate_data
temp_df$accel = accel

fit_unpenalized = bayes_fosr(accel ~ season_warm + sex_female + BMIZ + TV_g2hr + video_g1hr +
														 	mom_work_yes + asthma_yes + child_age + mom_age + educ_mom + num_rooms + 
														 	mom_born_US + tricep + subscap + skinfold, data = temp_df)

as_refundObj(fit_unpenalized$beta.hat[-1,]) %>% 
	ggplot(aes(x = index, y = value, group = id)) + geom_path(alpha = .5)
```

(Incidentally, as for FPCA analyses, the `refund.shiny` package has helpful tools for visualizing the results of a function-on-scalar regression analysis.)

```{r Accel_fosr_interactive, eval = FALSE}
plot_shiny(fit_unpenalized)
```

