---
title: "Function-on-Scalar Regression"
output:
  html_document: 
    code_folding: hide
    toc: true
    toc_float: true
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  fig.width = 8,
  fig.height = 4
)
```

This page contains a combination of traditional lecture materials (slides) and code demonstrating the relevant methods. The short course will proceed by working through both. We will use several recent packages in our examples; see the [About](./About.html) page for information about the package versions.

```{r setup}
library(tidyverse)
library(refund)
library(refund.shiny)

theme_set(theme_bw() + theme(legend.position = "bottom"))
```

In this section we'll use the [HeadStart data](./Data.html) to motivate the function-on-scalar regression model. Our main outcome of interest is the observed physical activity profile, with predictors including age, sex, and season. This material draws heavily from [Goldsmith et al](http://jeffgoldsmith.com/Downloads/HeadStart.pdf) (2016).


## Function-on-scalar regression

<script async class="speakerdeck-embed" data-id="337ceb9014d244a1a8b13282f00bae81" data-ratio="1.77777777777778" src="//speakerdeck.com/assets/embed.js"></script>
<div style="margin-bottom:5px"> <strong> <a href="https://speakerdeck.com/jeffgoldsmith/icampam-notation" title="ICAMPAM Short Course: FoSR" target="_blank">ICAMPAM Short Course: FoSR</a> </strong> from <strong><a href="https://speakerdeck.com/jeffgoldsmith" target="_blank">Jeff Goldsmith</a></strong>. </div>


## Practical example

One use of the rainbow plot is to get a quick sense for whether functional responses are related to covariates. Below we plot activity curves according to the season in which they were observed. Because the data are noisy enough that trends are not immediately apparent, we also include smooth means for both seasons.

```{r headstart_explore, eval = TRUE}
load("./DataCode/HeadStart.RDA")

as_refundObj(accel) %>% 
	left_join(dplyr::select(covariate_data, id, season)) %>%
	ggplot(aes(x = index, y = value, group = id, color = season)) + geom_path(alpha = .1) +
	geom_smooth(aes(group = season), se = FALSE)
```

Based on the above, we fit the FoSR equivalent of a simple linear regression to these data. 

```{r headstart_fosr_slr, eval = TRUE}
temp_df = covariate_data
temp_df$accel = accel

fosr_slr = bayes_fosr(accel ~ season, data = temp_df, 
											est.method = "GLS", Kt = 8, basis = "pbs")

as_refundObj(fosr_slr$beta.hat) %>% 
	ggplot(aes(x = index, y = value)) + facet_grid(~id) + geom_path()
```

The `refund.shiny` package has helpful tools for visualizing the results of a function-on-scalar regression analysis; these can be helpful for understanding the results. 

```{r headstart_fosr_slr_interactive, eval = FALSE}
plot_shiny(fosr_slr)
```

To examine more complex associations, and to account for possible confounding, we use the FoSR equivalent of a multiple linear regression.

```{r headstart_fosr_mlr, eval = TRUE}
fosr_mlr = bayes_fosr(accel ~ season + sex + BMIZ + TV + 
                      videogames + mom_work + asthma + child_age + 
                      mom_age + educ_mom + num_rooms + mom_born_US + tricep + 
                      subscap + skinfold, data = temp_df, 
											est.method = "GLS", Kt = 8, basis = "pbs")

as_refundObj(fosr_mlr$beta.hat[-1,]) %>% 
	ggplot(aes(x = index, y = value, group = id)) + geom_path(alpha = .5)
```

Again, the results of this model can be easier to understand using interactive graphics.

```{r headstart_fosr_mlr_interactive, eval = FALSE}
plot_shiny(fosr_mlr)
```

For these same data, we can compute average activity counts for each subject and fit a usual MLR. 

```{r headstart_comparison, eval = TRUE}
temp_df = covariate_data
temp_df$mean_accel = apply(accel, 1, mean)

mlr = lm(mean_accel ~ season + sex + BMIZ + TV + 
                      videogames + mom_work + asthma + child_age + 
                      mom_age + educ_mom + num_rooms + mom_born_US + tricep + 
                      subscap + skinfold, data = temp_df)

summary(mlr) %>% 
	broom::tidy() %>%
	knitr::kable(digits = 2)
```

The table below compares the results of the MLR to the integrated coefficients in the FoSR.

```{r headstart_comparison_table, eval = TRUE}
table.compare = data.frame(beta.mlr = coef(mlr),
                           beta.fosr = apply(fosr_mlr$beta.hat, 1, mean))

knitr::kable(table.compare, digits = 2)
```
