---
title: "Notation for FDA"
output:
  html_document: 
    code_folding: hide
    toc: true
    toc_float: true
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  fig.width = 8,
  fig.height = 4
)
```

This page contains a combination of traditional lecture materials (slides) and code demonstrating the relevant methods. The short course will proceed by working through both. We will use several recent packages in our examples; see the [About](./About.html) page for information about the package versions.

```{r setup}

library(tidyverse)
library(refund.shiny)

theme_set(theme_bw() + theme(legend.position = "bottom"))
```

## Notation for functional data

<script async class="speakerdeck-embed" data-id="22db63f1cf324ec6b998c631191af6ed" data-ratio="1.33333333333333" src="//speakerdeck.com/assets/embed.js"></script>
<div style="margin-bottom:5px"> <strong> <a href="https://speakerdeck.com/jeffgoldsmith/icampam-notation" title="ICAMPAM Short Course: Notation for FDA" target="_blank">ICAMPAM Short Course: Notation for FDA</a> </strong> from <strong><a href="https://speakerdeck.com/jeffgoldsmith" target="_blank">Jeff Goldsmith</a></strong>. </div>

## Practical example

In this section we will use the HeadStart dataset as an example to review notation and demonstrate useful plots of functional data. The code below loads this dataset.

```{r headstart_load, eval = TRUE}

load("./DataCode/HeadStart.RDA")

```

First, we plot a single subject to illustrate the "functional" nature of these data. 

```{r headstart_onesubj, eval = TRUE}

as_refundObj(accel) %>% 
	filter(id == 1) %>%
	ggplot(aes(x = index, y = value)) + geom_path()

```

Next, we plot all subjects. The previous plot is a single noodle in this plot of spaghetti.

```{r headstart_spaghetti, eval = TRUE}

as_refundObj(accel) %>% 
	ggplot(aes(x = index, y = value, group = id)) + geom_path(alpha = .1)

```

Now we compute the mean at each time point separately, and add this to our spaghetti. 

```{r headstart_pw_mean, eval = TRUE}

pw_mean = as_refundObj(accel) %>%
	group_by(index) %>%
	summarize(pw_mean = mean(value))

as_refundObj(accel) %>% 
	ggplot(aes(x = index, y = value, group = id)) + geom_path(alpha = .1) +
	geom_path(data = pw_mean, aes(y = pw_mean, group = NULL), color = "red", size = 1)

```

The pointwise mean is a bit jagged; now we use a smooth mean estimate.

```{r headstart_smooth_mean, eval = TRUE}

as_refundObj(accel) %>% 
	ggplot(aes(x = index, y = value, group = id)) + geom_path(alpha = .1) +
	geom_smooth(aes(group = NULL), color = "red", size = 1) 

```

Rainbow plots color each noodle according to some covariate value. We illustrate this using BMI Z-score. 

```{r headstart_rainbow, eval = TRUE}

as_refundObj(accel) %>% 
	left_join(dplyr::select(covariate_data, id, BMIZ)) %>%
	ggplot(aes(x = index, y = value, group = id, color = BMIZ)) + geom_path(alpha = .5) + 
  scale_colour_gradientn(colours = c("red","yellow","green","lightblue","darkblue"),
                         values = c(1.0, 0.6, 0.55, 0.45, 0.4, 0))

```

Lastly, we show the covariance surface to get an idea of the overall variance and the correlation across times. 

```{r headstart_covariance, eval = TRUE, fig.height = 5, fig.width = 7}

library(plotly)

covariance = cov(accel)
plot_ly(z = ~covariance) %>% add_surface()

```
